A Large-Scale Study of Polymorphism in R

### 2019-04-06 paper/main.tex
smol update

Now, what makes these so polymorphic?
The first package, magrittr, is one that we discussed earlier in the context of its pipe \%$>$\% function. 
It's not surprising that the package as a whole is quite polymorphic, as it implements {\it several} different pipe functions, e.g. \%$<>$\% which pipes as normal and then assigns to the left-hand argument.
In fact, all but knitLatex implement some form of metaprogramming:
oshka meta
\begin{enumerate}

	\item knitLatex: two functions are largely responsible for this level of polymorphism: sTab, which produces \LaTeX \xspace supertabular environments, and lTab, which produces \LaTeX \xspace longtable environments.
	These functions both have over 15 arguments, and there are a large number of recorded configurations, with many of the arguments being optional.

	\item

	\item

>>>>

Now, what makes these so polymorphic?
The first package, magrittr, is one that we discussed earlier in the context of its pipe \%$>$\% function. 
It's not surprising that the package as a whole is quite polymorphic, as it implements {\it several} different pipe functions, e.g. \%$<>$\% which pipes as normal and then assigns to the left-hand argument.
In fact, all but knitLatex implement some form of metaprogramming:
oshka metaprograms in the same style as Tidyverse, scatterD3 metaprograms on plot objects, and yaml converts R expressions to YAML expressions.
This is a trend we have observed: {\it the most polymorphic functions in R are metaprogramming their arguments}.
